---
title: "p8105_hw1_jdv2118"
output: github_document
---

```{r}
library(tidyverse)
```

# Problem 2

## Creating a dataframe 

This is a dataframe called "problem_2_df" that was created and it is comprised of a random sample, logical vector, character vector, and factor vector.

```{r}

problem_2_df =
  tibble(
    random_sample = rnorm(n = 10, mean = 0, sd = 1),
    logical_vector = random_sample > 0,
    character_vector = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_vector = factor(c("low", "medium", "high", "low", "medium", "high", "low", "medium", "high",       "low"))
  )
```

## Computing a mean of each variable in the dataframe

The mean of the "random_sample" variable is `r mean(pull(problem_2_df, random_sample))`.  The mean of the "logical_vector" variable is `r mean(pull(problem_2_df, logical_vector))`.  The mean of the "character_vector" variable cannot be computed as it is not a numeric or logical variable.  The mean of the "character_vector" variable is computed as `r mean(pull(problem_2_df, character_vector))`. The mean of the "factor_vector" variable cannot be computed as it is not a numeric or logical variable.  The mean of the "factor_vector" variable is computed as `r mean(pull(problem_2_df, character_vector))`.  

```{r}

mean(pull(problem_2_df, random_sample))

mean(pull(problem_2_df, logical_vector))

mean(pull(problem_2_df, character_vector))

mean(pull(problem_2_df, factor_vector))
```

## Converting variables from one type to another

The following code changes the logical variable to a numeric variable.  The following code also changes the factor variable to a numeric variable.  However, the following code is not able to change the character variable to a numeric variable, which explains why I cannot compute the mean from the character variable.  I can only compute means from numeric and logical variables.  I can compute a mean from a factor variable if it is converted to a numeric variable.  I cannot compute means from character variables as this variable type cannot be converted to a numeric variable.

```{r, eval = FALSE}

as.numeric(pull(problem_2_df, logical_vector))

as.numeric(pull(problem_2_df, character_vector))

as.numeric(pull(problem_2_df, factor_vector))
```


